---
title: "VisitorsTSAnalysis"
author: "Sandhya Amaresh"
date: "July 20, 2016"
output: 
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
#### This is a R Markdown file to plot the TS for the Visitors dataset
#### Plot the time series. Can you identify seasonal fluctuations and/or a trend?
```{r}
library(fpp)
data("visitors")
plot(visitors)
```
#### Use a classical decomposition to calculate the trend-cycle and seasonal indices. 
#### Do the results support the graphical interpretation from part (a)? 
```{r}
fitd <- decompose(visitors)
plot(fitd)
```
####Compute and plot the seasonally adjusted data.
```{r}
eeadj <- seasadj(fitd)
plot(eeadj)
```
#### Change one observation to be an outlier (e.g., add 500 to one observation), and recompute the seasonally adjusted data. What is the effect of the outlier? 
```{r}
visitors2 <- ts(c(visitors[1:54],visitors[55]+200,visitors[56:240]),start=c(1985,5),frequency=12)
plot(visitors2)
fitd2 <- decompose(visitors2)
eeadj2 <- seasadj(fitd2)
plot(eeadj2)
plot(eeadj)
lines(eeadj2,type="l",col="red")
```
#### Does it make any difference if the outlier is near the end rather than in the middle of the time series? 
```{r}
visitors3 <- ts(c(visitors[1:239],visitors[240]+200),start=c(1985,5),frequency=12)
fitd3 <- decompose(visitors3)
eeadj3 <- seasadj(fitd3)
plot(eeadj3)
lines(eeadj2,type="l",col="red")
```
####Now use STL to decompose the series. 
```{r}
fit <- stl(visitors, s.window=5)
plot(fit)
plot(visitors, col="gray",
      main="Visitors",
      ylab="New Visitors", xlab="")
lines(fit$time.series[,2],col="red",ylab="Trend")
```
